Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case

### 2019-05-08 ICML-camera-ready/main-all.tex
add camera-ready folder
pushed the scaling into the proof of Theorem 8
change some figures

\bibliography{biblio}
\bibliographystyle{icml2019}

% For actual submission remove everything below.
% Use appendices only in supplementray material.
\appendix
\clearpage

>>>>

\section*{Acknowledgments} We thank Francesco Orabona and Wen Sun
for helpful initial discussions, and thank Adam Klivans and Rocco Servedio for helpful
discussions on~\citep{Klivans-Servedio-2008} and
pointing out the reference~\citep{Klivans-Servedio-2004}. We also thank Dylan Foster, 
Akshay Krishnamurthy, and Haipeng Luo for providing a candidate solution to our problem.

\bibliography{biblio}
%\bibliographystyle{plainnat}
\bibliographystyle{icml2019}

% For actual submission remove everything below.
% Use appendices only in supplementray material.
\onecolumn
\appendix
\clearpage
